\textit{Red Oak}: Proactive Policy Generation

### 2015-05-10 draft.tex
pretty printing

\begin{figure*}[ht]
\begin{lstlisting}
let compile (f: packet -> forwarding_decision) : policy =
      push most general packet to (empty) stack
      set the current location to be the root of an empty decision tree
      while (stack is not empty)
         pop the top of the stack as pkt
         run f of pkt resulting in a forwarding decision fd (and a modified packet pkt)
         record the forwarding decision for the symbolic packet pkt at the current location in the decision tree
         set the current location to be the root of the decision tree and repeat

@@

\begin{figure*}[ht]
\begin{lstlisting}
let run (pol: policy) (inputs: ((field*int) list) list) : unit =
      build the symbolic rules for policy pol
      generate the concrete rules with all relations empty
      for each packets in input,
          find the first of the current rule matching the packet, and record the forwarding decision fd
          if packet is sent to the controller then
              evaluate the policy on the packet, potentially adding or removing tuples from relations, record forwarding decision fd'
              regenerate concrete rules
              forward the packet according the forwarding decision fd'
          else
              forward the packet according to fd 
\end{lstlisting}

@@

% probably no evaluation :(
\section*{Evaluation}
% 1) optimality w.r.t. packets seen by the controler?
% 2) more examples
% 3) simulated run

>>>>

\begin{figure*}[ht]
\begin{lstlisting}
let compile (f: packet -> forwarding_decision) : policy =
      push most general packet to (empty) stack
      set the current location to be the root of an empty decision tree
      while (stack is not empty)
         pop the top of the stack as pkt
         run f of pkt resulting in a forwarding decision fd and a refined packet pkt
         record the forwarding decision for the symbolic packet pkt in the decision tree
         set the current location to be the root of the decision tree and repeat

@@

\begin{figure*}[ht]
\begin{lstlisting}
let run (pol: policy) (inputs: ((field*int) list) list) : unit =
      build the symbolic rules for policy pol
      generate the concrete rules with all relations empty
      for each packets in input,
          find the first rule matching the packet, and record the forwarding decision fd
          if packet is sent to the controller then
              evaluate the policy on the packet, potentially updating relations
              regenerate concrete rules
              forward the packet according the evaluated forwarding decision
          else
              forward the packet according to fd 
\end{lstlisting}

@@

% probably no evaluation :(
% \section*{Evaluation}
% 1) optimality w.r.t. packets seen by the controler?
% 2) more examples
% 3) simulated run
